

Loading libraries:

```{r}
library("tidyverse")
library("dplyr")
library("lubridate")
library("linelist")
library("plyr")
library("gtools")
library("car")
library("stargazer")
library("data.table")
library("ggpubr")
library("writexl")
library("rstatix")
library("jtools")
library("huxtable")
library("aod")
library("olsrr")

``` 

Loading and preparing data:

```{r}
attach(BoardexEU)
BoardexEU$Sector = as.factor(Sector)
BoardexEU$DateStartRole = as.character(BoardexEU$DateStartRole)
BoardexEU$DateEndRole = as.character(BoardexEU$DateEndRole)
BoardexEU$DateStartRole=as.Date(DateStartRole,format = "%Y%m%d")
BoardexEU$DateEndRole= as.Date(DateEndRole,format = "%Y%m%d")
BoardexEU$DateEndRole[is.na(BoardexEU$DateEndRole)] = as.Date("2100/06/01", formate = "Y%/m%/d%")
BoardexEU$DateStartRole[is.na(BoardexEU$DateStartRole)] = as.Date("1900/06/01", formate = "Y%/m%/d%")




```

Creating a list of directors who were employed by the government:

```{r}

directors_ex_gov_df = BoardexEU %>% filter(BoardexEU$OrgType == "Government")
directors_ex_gov_df_unq = distinct(directors_ex_gov_df, directors_ex_gov_df$DirectorID, .keep_all = TRUE)
drops=c("directors_ex_gov_df$directors_ex_gov_id")
directors_ex_gov_df_unq = directors_ex_gov_df_unq[ , !(names(directors_ex_gov_df_unq) %in% drops)]
directors_ex_gov_df_inter = interval(start = directors_ex_gov_df$DateStartRole, end = directors_ex_gov_df$DateEndRole)
directors_ex_gov_df_int = data.frame(directors_ex_gov_df, directors_ex_gov_df_inter)
directors_ex_gov_df_int_unq = directors_ex_gov_df_int[order(directors_ex_gov_df_int$DateStartRole),]
directors_ex_gov_df_int_unq = distinct(directors_ex_gov_df_int, directors_ex_gov_df_int$DirectorID,.keep_all = TRUE)
directors_ex_gov_df_int_unq = directors_ex_gov_df_int_unq[ , !(names(directors_ex_gov_df_int_unq) %in% c("directors_ex_gov_df_int$DirectorID"))]
attach(directors_ex_gov_df_int_unq)
director_check_final = data.frame(DirectorID,DateEndRole,DateStartRole)
```

Formatting the data describing oragnizations:

```{r}
Company_df_EU$AnnualReportDate =as.Date(Company_df_EU$AnnualReportDate, format = "%Y/%m/%d")
Company_df_EU$HOCountryName[Company_df_EU$HOCountryName== "United Kingdom - England"] =  "United Kingdom"
Company_df_EU = Company_df_EU %>% mutate(political_career = as.numeric(as.character( Company_df_EU$DirectorID) %in% as.character( directors_ex_gov_df_unq$DirectorID)))
df_final=merge(Company_df_EU,director_check_final, by = "DirectorID")
Company_df_EU = Company_df_EU %>% mutate(DateEndRole = as.Date("2100/01/01", formate = "Y%/m%/d%"))
Company_df_EU = Company_df_EU %>% mutate(DateStartRole = as.Date("2100/01/01", formate = "Y%/m%/d%"))
cc = rbind(df_final,Company_df_EU)
cc = subset(cc, select = -c(RowType))
Company_df_EU_updated = distinct(cc,cc[1:7],.keep_all = TRUE)
political_career_after =as.numeric(Company_df_EU_updated$DateEndRole<Company_df_EU_updated$AnnualReportDate)
political_career_during = as.numeric(Company_df_EU_updated$AnnualReportDate %within%   (interval(start = Company_df_EU_updated$DateStartRole, end = Company_df_EU_updated$DateEndRole)))
political_career_both=(political_career_after+political_career_during)
Company_df_EU_updated = data.frame(Company_df_EU_updated, as.numeric(political_career_after),political_career_during,political_career_both)
Company_df_EU_updated$political_career_both[is.na(Company_df_EU_updated$political_career_both)] = 0
Company_df_EU_updated = Company_df_EU_updated %>% mutate(board_id_factor = as.factor(Company_df_EU_updated$BoardID))
Company_df_EU_updated = Company_df_EU_updated %>% mutate(year_factor = as.factor(year(Company_df_EU_updated$AnnualReportDate)))
Company_df_EU_updated = Company_df_EU_updated %>% mutate(country_factor = as.factor(Company_df_EU_updated$HOCountryName))

```


Loading and preparing data:

```{r}
attach(BoardexUK)
BoardexUK$Sector = as.factor(Sector)
BoardexUK$DateStartRole = as.character(BoardexUK$DateStartRole)
BoardexUK$DateEndRole = as.character(BoardexUK$DateEndRole)
BoardexUK$DateStartRole=as.Date(DateStartRole,format = "%Y%m%d")
BoardexUK$DateEndRole= as.Date(DateEndRole,format = "%Y%m%d")
BoardexUK$DateEndRole[is.na(BoardexUK$DateEndRole)] = as.Date("2100/06/01", formate = "Y%/m%/d%")
BoardexUK$DateStartRole[is.na(BoardexUK$DateStartRole)] = as.Date("1900/06/01", formate = "Y%/m%/d%")



```

Creating a list of directors who were employed by the government:

```{r}


directors_ex_gov_df = BoardexUK %>% filter(BoardexUK$OrgType == "Government")
directors_ex_gov_df_unq = distinct(directors_ex_gov_df, directors_ex_gov_df$DirectorID, .keep_all = TRUE)
drops=c("directors_ex_gov_df$directors_ex_gov_id")
directors_ex_gov_df_unq = directors_ex_gov_df_unq[ , !(names(directors_ex_gov_df_unq) %in% drops)]
directors_ex_gov_df_inter = interval(start = directors_ex_gov_df$DateStartRole, end = directors_ex_gov_df$DateEndRole)
directors_ex_gov_df_int = data.frame(directors_ex_gov_df, directors_ex_gov_df_inter)
directors_ex_gov_df_int_unq = directors_ex_gov_df_int[order(directors_ex_gov_df_int$DateStartRole),]
directors_ex_gov_df_int_unq = distinct(directors_ex_gov_df_int, directors_ex_gov_df_int$DirectorID,.keep_all = TRUE)
directors_ex_gov_df_int_unq = directors_ex_gov_df_int_unq[ , !(names(directors_ex_gov_df_int_unq) %in% c("directors_ex_gov_df_int$DirectorID"))]
attach(directors_ex_gov_df_int_unq)
director_check_final = data.frame(DirectorID,DateEndRole,DateStartRole)

```

Formatting the data describing oragnizations:

```{r}
Company_df_UK$AnnualReportDate =as.Date(Company_df_UK$AnnualReportDate, format = "%Y/%m/%d")
Company_df_UK$HOCountryName[Company_df_UK$HOCountryName== "United Kingdom - England"] =  "United Kingdom"
Company_df_UK$HOCountryName[Company_df_UK$HOCountryName== "United Kingdom - Wales"] =  "United Kingdom"
Company_df_UK$HOCountryName[Company_df_UK$HOCountryName== "United Kingdom - Scotland"] =  "United Kingdom"
Company_df_UK$HOCountryName[Company_df_UK$HOCountryName== "United Kingdom - Northern Ireland"] =  "United Kingdom"
Company_df_UK = Company_df_UK %>% mutate(political_career = as.numeric(as.character( Company_df_UK$DirectorID) %in% as.character( directors_ex_gov_df_unq$DirectorID)))
df_final=merge(Company_df_UK,director_check_final, by = "DirectorID")
Company_df_UK = Company_df_UK %>% mutate(DateEndRole = as.Date("2100/01/01", formate = "Y%/m%/d%"))
Company_df_UK = Company_df_UK %>% mutate(DateStartRole = as.Date("2100/01/01", formate = "Y%/m%/d%"))
cc = rbind(df_final,Company_df_UK)
cc = subset(cc, select = -c(RowType))
Company_df_UK_updated = distinct(cc,cc[1:7],.keep_all = TRUE)
political_career_after =as.numeric(Company_df_UK_updated$DateEndRole<Company_df_UK_updated$AnnualReportDate)
political_career_during = as.numeric(Company_df_UK_updated$AnnualReportDate %within%   (interval(start = Company_df_UK_updated$DateStartRole, end = Company_df_UK_updated$DateEndRole)))
political_career_both=(political_career_after+political_career_during)
Company_df_UK_updated = data.frame(Company_df_UK_updated, as.numeric(political_career_after),political_career_during,political_career_both)
Company_df_UK_updated$political_career_both[is.na(Company_df_UK_updated$political_career_both)] = 0
Company_df_UK_updated = Company_df_UK_updated %>% mutate(board_id_factor = as.factor(Company_df_UK_updated$BoardID))
Company_df_UK_updated = Company_df_UK_updated %>% mutate(year_factor = as.factor(year(Company_df_UK_updated$AnnualReportDate)))
Company_df_UK_updated = Company_df_UK_updated %>% mutate(country_factor = as.factor(Company_df_UK_updated$HOCountryName))
```

Loading and preparing data:

```{r}

attach(BoardexRest)
BoardexRest$Sector = as.factor(Sector)
BoardexRest$DateStartRole = as.character(BoardexRest$DateStartRole)
BoardexRest$DateEndRole = as.character(BoardexRest$DateEndRole)
BoardexRest$DateStartRole=as.Date(DateStartRole,format = "%Y%m%d")
BoardexRest$DateEndRole= as.Date(DateEndRole,format = "%Y%m%d")
BoardexRest$DateEndRole[is.na(BoardexRest$DateEndRole)] = as.Date("2100/06/01", formate = "Y%/m%/d%")
BoardexRest$DateStartRole[is.na(BoardexRest$DateStartRole)] = as.Date("1900/06/01", formate = "Y%/m%/d%")




```

Creating a list of directors who were employed by the government:

```{r}

directors_ex_gov_df = BoardexRest %>% filter(BoardexRest$OrgType == "Government")
directors_ex_gov_df_unq = distinct(directors_ex_gov_df, directors_ex_gov_df$DirectorID, .keep_all = TRUE)
drops=c("directors_ex_gov_df$directors_ex_gov_id")
directors_ex_gov_df_unq = directors_ex_gov_df_unq[ , !(names(directors_ex_gov_df_unq) %in% drops)]
directors_ex_gov_df_inter = interval(start = directors_ex_gov_df$DateStartRole, end = directors_ex_gov_df$DateEndRole)
directors_ex_gov_df_int = data.frame(directors_ex_gov_df, directors_ex_gov_df_inter)
directors_ex_gov_df_int_unq = directors_ex_gov_df_int[order(directors_ex_gov_df_int$DateStartRole),]
directors_ex_gov_df_int_unq = distinct(directors_ex_gov_df_int, directors_ex_gov_df_int$DirectorID,.keep_all = TRUE)
directors_ex_gov_df_int_unq = directors_ex_gov_df_int_unq[ , !(names(directors_ex_gov_df_int_unq) %in% c("directors_ex_gov_df_int$DirectorID"))]
attach(directors_ex_gov_df_int_unq)
director_check_final = data.frame(DirectorID,DateEndRole,DateStartRole)
```

Formatting the data describing oragnizations:

```{r}
Company_df_Rest$AnnualReportDate =as.Date(Company_df_Rest$AnnualReportDate, format = "%Y/%m/%d")
Company_df_Rest$HOCountryName[Company_df_EU$HOCountryName== "Korea Republic Of (South Korea)"] =  "South Korea"
Company_df_Rest = Company_df_Rest %>% mutate(political_career = as.numeric(as.character( Company_df_Rest$DirectorID) %in% as.character( directors_ex_gov_df_unq$DirectorID)))
df_final=merge(Company_df_Rest,director_check_final, by = "DirectorID")
Company_df_Rest = Company_df_Rest %>% mutate(DateEndRole = as.Date("2100/01/01", formate = "Y%/m%/d%"))
Company_df_Rest = Company_df_Rest %>% mutate(DateStartRole = as.Date("2100/01/01", formate = "Y%/m%/d%"))
cc = rbind(df_final,Company_df_Rest)
cc = subset(cc, select = -c(RowType))
Company_df_Rest_updated = distinct(cc,cc[1:7],.keep_all = TRUE)
political_career_after =as.numeric(Company_df_Rest_updated$DateEndRole<Company_df_Rest_updated$AnnualReportDate)
political_career_during = as.numeric(Company_df_Rest_updated$AnnualReportDate %within%   (interval(start = Company_df_Rest_updated$DateStartRole, end = Company_df_Rest_updated$DateEndRole)))
political_career_both=(political_career_after+political_career_during)
Company_df_Rest_updated = data.frame(Company_df_Rest_updated, as.numeric(political_career_after),political_career_during,political_career_both)
Company_df_Rest_updated$political_career_both[is.na(Company_df_Rest_updated$political_career_both)] = 0
Company_df_Rest_updated = Company_df_Rest_updated %>% mutate(board_id_factor = as.factor(Company_df_Rest_updated$BoardID))
Company_df_Rest_updated = Company_df_Rest_updated %>% mutate(year_factor = as.factor(year(Company_df_Rest_updated$AnnualReportDate)))
Company_df_Rest_updated = Company_df_Rest_updated %>% mutate(country_factor = as.factor(Company_df_Rest_updated$HOCountryName))
```

Loading and preparing data:

```{r}

attach(BoardexNA)
BoardexNA$Sector = as.factor(Sector)
BoardexNA$DateStartRole = as.character(BoardexNA$DateStartRole)
BoardexNA$DateEndRole = as.character(BoardexNA$DateEndRole)
BoardexNA$DateStartRole=as.Date(DateStartRole,format = "%Y%m%d")
BoardexNA$DateEndRole= as.Date(DateEndRole,format = "%Y%m%d")
BoardexNA$DateEndRole[is.na(BoardexNA$DateEndRole)] = as.Date("2100/06/01", formate = "Y%/m%/d%")
BoardexNA$DateStartRole[is.na(BoardexNA$DateStartRole)] = as.Date("1900/06/01", formate = "Y%/m%/d%")




```

Creating a list of directors who were employed by the government:

```{r}
directors_ex_gov_df = BoardexNA %>% filter(BoardexNA$OrgType == "Government")
directors_ex_gov_df_unq = distinct(directors_ex_gov_df, directors_ex_gov_df$DirectorID, .keep_all = TRUE)
drops=c("directors_ex_gov_df$directors_ex_gov_id")
directors_ex_gov_df_unq = directors_ex_gov_df_unq[ , !(names(directors_ex_gov_df_unq) %in% drops)]
directors_ex_gov_df_inter = interval(start = directors_ex_gov_df$DateStartRole, end = directors_ex_gov_df$DateEndRole)
directors_ex_gov_df_int = data.frame(directors_ex_gov_df, directors_ex_gov_df_inter)
directors_ex_gov_df_int_unq = directors_ex_gov_df_int[order(directors_ex_gov_df_int$DateStartRole),]
directors_ex_gov_df_int_unq = distinct(directors_ex_gov_df_int, directors_ex_gov_df_int$DirectorID,.keep_all = TRUE)
directors_ex_gov_df_int_unq = directors_ex_gov_df_int_unq[ , !(names(directors_ex_gov_df_int_unq) %in% c("directors_ex_gov_df_int$DirectorID"))]
attach(directors_ex_gov_df_int_unq)
director_check_final = data.frame(DirectorID,DateEndRole,DateStartRole)
```

Formatting the data describing oragnizations:

```{r}
Company_df_NA$AnnualReportDate =as.Date(Company_df_NA$AnnualReportDate, format = "%Y/%m/%d")
Company_df_NA = Company_df_NA %>% mutate(political_career = as.numeric(as.character( Company_df_NA$DirectorID) %in% as.character( directors_ex_gov_df_unq$DirectorID)))
df_final=merge(Company_df_NA,director_check_final, by = "DirectorID")
Company_df_NA = Company_df_NA %>% mutate(DateEndRole = as.Date("2100/01/01", formate = "Y%/m%/d%"))
Company_df_NA = Company_df_NA %>% mutate(DateStartRole = as.Date("2100/01/01", formate = "Y%/m%/d%"))
cc = rbind(df_final,Company_df_NA)
Company_df_NA_updated = distinct(cc,cc[1:7],.keep_all = TRUE)
political_career_after =as.numeric(Company_df_NA_updated$DateEndRole<Company_df_NA_updated$AnnualReportDate)
political_career_during = as.numeric(Company_df_NA_updated$AnnualReportDate %within%   (interval(start = Company_df_NA_updated$DateStartRole, end = Company_df_NA_updated$DateEndRole)))
political_career_both=(political_career_after+political_career_during)
Company_df_NA_updated = data.frame(Company_df_NA_updated, as.numeric(political_career_after),political_career_during,political_career_both)
Company_df_NA_updated$political_career_both[is.na(Company_df_NA_updated$political_career_both)] = 0
Company_df_NA_updated = Company_df_NA_updated %>% mutate(board_id_factor = as.factor(Company_df_NA_updated$BoardID))
Company_df_NA_updated$ISIN = gsub("US","",Company_df_NA_updated$ISIN)
Company_df_NA_updated$ISIN = gsub("CA","",Company_df_NA_updated$ISIN)
Company_df_NA_updated = Company_df_NA_updated %>% mutate(year_factor = as.factor(year(Company_df_NA_updated$AnnualReportDate)))
Company_df_NA_updated = Company_df_NA_updated %>% mutate(country_factor = as.factor(Company_df_NA_updated$HOCountryName))

```





Combining datasets:
```{r}
Company_df_UK_updated = subset(Company_df_UK_updated,select = -c(CompanyID))
Company_df_EU_updated = subset(Company_df_EU_updated,select = -c(CompanyID))

df_EU = Company_df_EU_updated
df_UK = Company_df_UK_updated
df_Rest = Company_df_Rest_updated
df_NA = Company_df_NA_updated
df_omega = smartbind(df_EU,df_UK,df_Rest,df_NA)
df_omega$country_factor = as.factor(df_omega$HOCountryName)
df_omega = subset(df_omega,select = -c(Ticker))
length(unique(df_omega$BoardID))

rm(list=setdiff(ls(), c("df_omega", "Compustat_NA", "Compustat_Rest","Index","regdata_4_0_industries")))

Average_by_country_all = data.frame(with(df_omega, tapply(political_career_both, country_factor, mean)))
df_omega = mutate_all(df_omega, list(~na_if(.,"")))
sum(is.na(df_omega$ISIN))/length(df_omega$ISIN)
df_omega_wo_isin_na = na.omit(df_omega)
```

Compustat db:
```{r}
Compustat_NA$ISIN = Compustat_NA$cusip
Compustat_NA_upd = subset(Compustat_NA, select = c("gvkey","fyear","act","ebitda","emp","ISIN","naics"))
names(Compustat_Rest)[8]="ISIN"
Compustat_Rest_upd = subset(Compustat_Rest, select = c("gvkey","fyear","act","ebitda","emp","ISIN","naics"))
Compustat_full = rbind(Compustat_NA_upd,Compustat_Rest_upd)
Compustat_full$year_factor = as.factor(Compustat_full$fyear)
Compustat_full_db =data.table(Compustat_full, key=c("ISIN","year_factor"))
Compustat_full_db = mutate_all(Compustat_full_db, list(~na_if(.,"")))
df_omega_wo_isin_na=data.table(df_omega_wo_isin_na, key = c("ISIN","year_factor"))
compustat_boardex_merged = merge(df_omega_wo_isin_na, Compustat_full_db)
compustat_boardex_merged_wo_na = na.omit(compustat_boardex_merged)


```


Standarizing emp variable
```{r}
attach(compustat_boardex_merged_wo_na)
compustat_boardex_merged_wo_na = compustat_boardex_merged_wo_na %>% mutate(emp_log = log(compustat_boardex_merged_wo_na$emp))
MEAN_emp = aggregate(emp_log ~  + year_factor+country_factor, data=compustat_boardex_merged_wo_na, FUN=mean)
Mean_emp=data.table(MEAN_emp, key=c("country_factor","year_factor"))
SD_emp = aggregate(emp_log ~  + year_factor+country_factor, data=compustat_boardex_merged_wo_na, FUN=sd)
SD_emp=data.table(SD_emp, key=c("country_factor","year_factor"))
emp_stats=merge(SD_emp,Mean_emp)
names(emp_stats)[3]="SD"
names(emp_stats)[4]="mean"
emp_stats=data.table(emp_stats,key=c("year_factor","country_factor"))
compustat_boardex_merged_wo_na = data.table(compustat_boardex_merged_wo_na, key=c("ISIN","year_factor","country_factor"))
compustat_emp= merge(emp_stats, compustat_boardex_merged_wo_na)
compustat_emp = compustat_emp %>% mutate(deviation_from_the_mean = ((compustat_emp$mean - compustat_emp$emp_log)/compustat_emp$SD))
ggdensity(compustat_emp$deviation_from_the_mean)



```

Standarizing act variable
```{r}
compustat_emp = compustat_emp %>% mutate(act_log = log(compustat_emp$act))
MEAN_act = aggregate(act_log ~  + year_factor+country_factor, data=compustat_emp, FUN=mean)
Mean_act=data.table(MEAN_act, key=c("country_factor","year_factor"))
SD_act = aggregate(act_log ~  + year_factor+country_factor, data=compustat_emp, FUN=sd)
SD_act=data.table(SD_act, key=c("country_factor","year_factor"))
act_log=merge(SD_act,Mean_act)
names(act_log)[3]="SD_act"
names(act_log)[4]="mean_act"
act_log=data.table(act_log,key=c("year_factor","country_factor"))
compustat_emp = data.table(compustat_emp, key=c("ISIN","year_factor","country_factor"))
compustat_act= merge(act_log, compustat_emp)
compustat_act = compustat_act %>% mutate(deviation_from_the_mean_act = ((compustat_act$mean_act - compustat_act$act_log)/compustat_act$SD_act))

```


Standarizing ebitda variable
```{r}
compustat_act = compustat_act %>% mutate(ebitda_log = log(compustat_act$ebitda))
MEAN_ebitda = aggregate(ebitda_log ~  + year_factor+country_factor, data=compustat_act, FUN=mean)
MEAN_ebitda=data.table(MEAN_ebitda, key=c("country_factor","year_factor"))
SD_ebitda = aggregate(ebitda_log ~  + year_factor+country_factor, data=compustat_act, FUN=sd)
SD_ebitda=data.table(SD_ebitda, key=c("country_factor","year_factor"))
ebitda_log=merge(SD_ebitda,MEAN_ebitda)
names(ebitda_log)[3]="SD_ebitda"
names(ebitda_log)[4]="mean_ebitda"
ebitda_log=data.table(ebitda_log,key=c("year_factor","country_factor"))
compustat_act = data.table(compustat_act, key=c("ISIN","year_factor","country_factor"))
compustat_ebitda= merge(ebitda_log, compustat_act)
compustat_ebitda = compustat_ebitda %>% mutate(deviation_from_the_mean_ebitda = ((compustat_ebitda$mean_ebitda - compustat_ebitda$ebitda_log)/compustat_ebitda$SD_ebitda))
```


```{r}
years = 2020:2002
years = append(years, seq(2000,1996,-2))
HOCountryName = Index[,1]
g = 0
for (i in 1:22){
  j = (5*i)-3
  f = j+5
  z = j+g
  h = f+g
if (i ==1){df = Index[,j:f]} else{df =  Index[,z:h]}
  colnames(df) = c("VA","PV","GE","RQ","RL","CC")
  g = g+1
  df = df %>% mutate(year_factor = as.factor(years[i]))
  df = data.frame(HOCountryName, df)
  if(i==1){df_whole = df} else{df_whole = rbind(df_whole,df)}
}
```

Merging two datasets:
```{r}
colnames(df_whole)[1] = "country_factor"
compustat_final = data.table(compustat_ebitda, key=c("year_factor", "country_factor", "ISIN"))
compustat_final$country_factor = as.character(compustat_final$country_factor)
compustat_final$country_factor[compustat_final$country_factor=="Bahamas"] = "Bahamas,The"
compustat_final$country_factor[compustat_final$country_factor=="CĂÂ´te D'ivoire"] = "Côte d'Ivoire"
compustat_final$country_factor[compustat_final$country_factor=="	Egypt"] = "Egypt, Arab Rep."
compustat_final$country_factor[compustat_final$country_factor=="Jersey"] = "Jersey, Channel Islands."
compustat_final$country_factor[compustat_final$country_factor=="Kyrgyzstan"] = "Kyrgyz Republic."
compustat_final$country_factor[compustat_final$country_factor=="	Macao SAR"] = "Macao SAR, China"
compustat_final$country_factor[compustat_final$country_factor=="Republic Of Ireland"] = "Ireland"
compustat_final$country_factor[compustat_final$country_factor=="	
Taiwan Territory of"] = "Taiwan, China"
compustat_final$country_factor[compustat_final$country_factor=="Hong Kong SAR"] = "Hong Kong SAR, China"
compustat_final$country_factor[compustat_final$country_factor=="Slovak Republic"] = "Slovakia"
compustat_final$country_factor[compustat_final$country_factor=="United Kingdom - England"] = "United Kingdom"
compustat_final$country_factor = as.factor(compustat_final$country_factor)
df_index = data.table(df_whole, key=c("country_factor","year_factor"))
df_prime = merge(df_index,compustat_ebitda)
df_prime$naics = as_factor(df_prime$naics)

```

Standarizing industry regulation
```{r}
regdata_4_0_industries = regdata_4_0_industries[-1,]
names(regdata_4_0_industries)[1:5] =  c("year_factor","industry_description","NAICS","industry_restrictions_1_0","industry_restrictions_2_0")
regdata_4_0_industries$industry_restrictions_1_0 = as.numeric(regdata_4_0_industries$industry_restrictions_1_0)
regdata_4_0_industries$industry_restrictions_2_0 = as.numeric(regdata_4_0_industries$industry_restrictions_2_0)
regdata = filter(regdata_4_0_industries, regdata_4_0_industries$year>=1996)
regdata = regdata %>% mutate(two_naics = substr(regdata$NAICS,1,2))
mean_restrictions_y = aggregate(industry_restrictions_1_0~ year_factor, data = regdata, FUN = mean)
sd_restrictions_y = aggregate(industry_restrictions_1_0~ year_factor, data = regdata, FUN = sd)
mean_restrictions = aggregate(industry_restrictions_1_0~ year_factor+two_naics, data = regdata, FUN = mean)
names(sd_restrictions_y)[2] = "sd_restrictions_y"
names(mean_restrictions_y)[2] = "mean_restrictions_y"
names(mean_restrictions)[3] = "mean_restrictions"
df_restrictions_y = cbind(mean_restrictions_y,sd_restrictions_y)
df_restrictions_y = df_restrictions_y[,-3]
mean_restrictions$year_factor = as.factor(mean_restrictions$year_factor)
mean_restrictions = data.table(mean_restrictions, key="year_factor")
df_restrictions_y = data.table(df_restrictions_y, key= "year_factor")
df_restrictions = merge(df_restrictions_y, mean_restrictions)
df_restrictions = data.table(df_restrictions, key = c("year_factor","two_naics"))
df_prime = df_prime %>% mutate(two_naics = substr(df_prime$naics,1,2))
df_prime = data.table(df_prime,key = c("year_factor","two_naics"))
df_prime = merge(df_prime, df_restrictions)
df_prime = df_prime %>% mutate(deviation_from_the_mean_restrictions = ((df_prime$mean_restrictions_y - df_prime$mean_restrictions)/df_prime$sd_restrictions_y))
naics = data.frame(unique(df_prime$two_naics))


```

Hypothesis check:
```{r}
df_prime$PV = as.numeric(df_prime$PV)
df_prime$GE = as.numeric(df_prime$GE)
df_prime$RQ = as.numeric(df_prime$RQ)
df_prime$CC = as.numeric(df_prime$CC)
Aggregate_VA = aggregate(VA ~ country_factor+year_factor, data = df_prime, FUN=mean)
Aggregate_PV = aggregate(PV ~ country_factor+year_factor, data = df_prime, FUN=mean)
Aggregate_GE = aggregate(GE ~ country_factor+year_factor, data = df_prime, FUN=mean)
Aggregate_RQ = aggregate(RQ ~ country_factor+year_factor, data = df_prime, FUN=mean)
Aggregate_CC = aggregate(CC ~ country_factor+year_factor, data = df_prime, FUN=mean)
Aggregate_pol = aggregate(political_career_both ~ country_factor+year_factor,data = df_prime,mean)
df_list = list(Aggregate_CC,Aggregate_GE,Aggregate_pol,Aggregate_PV,Aggregate_RQ,Aggregate_VA)
dff = df_list %>% reduce(full_join, by = c("country_factor","year_factor"))
dff = dff %>% mutate(PVsq = dff$PV^2)
dff100 = dff[,3:8]*100
dff100 = dff100 %>% mutate(PVsq = dff100$PV^2)
dff100 = dff100 %>% mutate(CCe = dff100$CC+1)
dff100$CCe = exp(1)^dff100$CCe
dff_merged = cbind(subset(dff, select=c("country_factor","year_factor")),dff100)
dff_merged = subset(dff_merged, select = - c(political_career_both))
political_avg = aggregate(political_career_both ~  + ISIN+year_factor+country_factor, data=df_prime, FUN=mean)
control_dt = data.table(subset(df_prime,select = c(ISIN, country_factor,year_factor,deviation_from_the_mean,deviation_from_the_mean_act,deviation_from_the_mean_ebitda,deviation_from_the_mean_restrictions)),key = c("ISIN","year_factor","country_factor"))
control_dt$deviation_from_the_mean[control_dt$deviation_from_the_mean =="NaN"] = "0"
control_dt$deviation_from_the_mean_act[control_dt$deviation_from_the_mean_act =="NaN"] = "0"
control_dt$deviation_from_the_mean_ebitda[control_dt$deviation_from_the_mean_ebitda =="NaN"] = "0"
dff_merged = data.table(dff_merged, key=c("country_factor","year_factor"))
df_salvation = merge(control_dt,political_avg)
df_salvation = merge(df_salvation,dff_merged)
df_salvation$deviation_from_the_mean = as.numeric(df_salvation$deviation_from_the_mean)
df_salvation$deviation_from_the_mean_act = as.numeric(df_salvation$deviation_from_the_mean_act)
df_salvation$deviation_from_the_mean_ebitda = as.numeric(df_salvation$deviation_from_the_mean_ebitda)
attach(df_salvation)
h5 = lm(political_career_both~VA+ PVsq+PV+ GE+ RQ+exp(CC) +deviation_from_the_mean+deviation_from_the_mean_act+deviation_from_the_mean_restrictions, data = df_salvation)
```


```{r}
correlations = data.frame(cor(df_salvation[,4:11]))
countries = data.frame(table(df_salvation$country_factor))
countries = countries %>% mutate(percentage = (countries$Freq/length(df_salvation$country_factor)*100))
politicians_avg = aggregate(political_career_both~ country_factor, data = df_salvation, FUN = mean)
countries$avg_politicians = politicians_avg$political_career_both*100
attach(countries)
countries = countries[order(countries$percentage, decreasing = TRUE),]
countries10 = countries[1:10,]
colnames(countries10) = c("Country", "Observations (Nr)","Observations (%)","Ex-gov officials (mean %)")
countries_list = data.frame(countries$Var1)
countries_list = data.frame(countries_list[order(countries_list$countries.Var1),])
  correlations = data.frame(cor(df_salvation[,4:13], use = "complete.obs"))
correlations = correlations %>% mutate(mean = colMeans(df_salvation[,4:13],na.rm = TRUE))
correlations = correlations %>% mutate(SD = sapply(df_salvation[,4:13], sd, na.rm=TRUE))
correlations_ordered = df_salvation[,c("political_career_both","VA","PV","GE","RQ","CC","deviation_from_the_mean","deviation_from_the_mean_act","deviation_from_the_mean_restrictions")]
mean = colMeans(correlations_ordered,na.rm = TRUE)
SD = sapply(correlations_ordered, sd, na.rm=TRUE)
correlations_final = data.frame(cor(correlations_ordered, use = "complete.obs"))
sd_mean = cbind(mean,SD)
correlations_ordered %>%
  select(political_career_both,VA,PV,GE,RQ,CC,deviation_from_the_mean,deviation_from_the_mean_act,deviation_from_the_mean_restrictions) %>%
  cor_mat() %>%
  cor_mark_significant() %>% 
  add_significance()
correlations_final = cbind(sd_mean,correlations_final)
effect_plot(h5,PVsq, interval = TRUE, y.label = "Nr of ex-government employees on the company's BOD (Percentage)", x.label = "Political Stability and Absence of Violance (Squared)", main.title = "Plotting Hypothesis 2")
wald.test(Sigma = vcov(h5), b= coef(h5), Terms = 1:6)
```
